---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nottshcOpenData

<!-- badges: start -->
<!-- badges: end -->

This package demonstrates some of the ways we use R.

## Installation

You can install the developmental version of `nottshcOpenData` using:

``` r
# install.packages("devtools")
devtools::install_github("CDU-data-science-team/nottshcOpenData")
```

You may also have to set up MySQL on your computer if it's not already installed, see https://db.rstudio.com/best-practices/drivers/ for more information.

## Example

This example demonstrates how the `nottshcOpenData` package can be used to 

**1.** connect to the server using `connect_mysql()`
**1.** query data from the database within R Studio using `get_px_exp()`
**1.** tidy the data on the database using `tidy_px_exp()`, and
**1.** load the data into the global environment using `dplyr::collect()`

```{r}
# Load public package
library(nottshcOpenData)
```

### 1. Connect to database

```{r}
# Create MySQL connection
# Note, the driver name, here "MySQL ODBC 8.0 ANSI Driver", may differ on your computer
conn_mysql_suce <- connect_mysql(database = "SUCE",
                                 driver = "MySQL ODBC 8.0 ANSI Driver")
```

### 2. Query data

```{r}
# Get database (db_) connection for specified date range 
db_px_data <- get_px_exp(from = "2020-01-01",
                         to = "2020-12-31")

# Look at messy data
db_px_data
```

### 3. Tidy data

```{r}
# Tidy the data (on the database)
# Next select some variables for this example
db_px_data_tidy <- db_px_data %>% 
  tidy_px_exp() %>% 
  dplyr::select(key, comment_key, date, team_c, team_n, directorate, division,
                category, subcategory, comment_type, comment_txt, crit)

# Look at tidy data
db_px_data_tidy
```

### 4. Collect data

In case the data needs to be loaded from the MySQL database into the global environment you can use the `collect()` function from the `dplyr` package.

```{r}
# Collect tidy data
df_px_data_tidy <- db_px_data_tidy %>% 
  dplyr::collect()

```

